%-------------------------
% Resume in Latex
% Author : Rahul Shamkuwar
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-8pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-8pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSingleItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2\vspace{-2pt} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-5pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-8pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Rahul Shamkuwar}} & Email : \href{mailto:rahulshamkuwar20@gmail.com}{rahulshamkuwar20@gmail.com}\\
  Denver, CO &  GitHub : \href{https://github.com/rahulshamkuwar}{rahulshamkuwar}\\
  Mobile : \href{tel:+6692820030}{+1-669-282-0030} & LinkedIn : \href{https://www.linkedin.com/in/rahulshamkuwar20}{rahulshamkuwar20} \\
\end{tabular*}\vspace{-5pt}


%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{University of Colorado Boulder}{Boulder, CO}
{Bachelor of Science in Computer Science;  GPA: 3.94}{Fall 2022 -- Fall 2024}\vspace{-2pt}
\resumeSubheading
{University of Illinois Urbana-Champaign}{Urbana-Champaign, IL}
{Bachelor of Science in Aerospace Engineering;  GPA: 3.46}{Fall 2020 -- Spring 2022}\vspace{-2pt}
\resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\section{Skills}
\resumeSubHeadingListStart
\resumeSubItem{Languages}
{Typescript, JavaScript, HTML, CSS, Python, Scala, Dart, C/C++, C\#, Java, SQL, NoSQL.}
\resumeSubItem{Technologies}
{Node.js, Nest.js, React, Next.js, Flutter, React Native, Tailwind, Swagger, Postman, pandas, NumPy, JupyterLab, Scikit-Learn, PyTorch, Optuna, TensorFlow, Keras, Jest.}
\resumeSubItem{Tools}
{AWS, OCI, Docker, GitHub Actions, Git, ESLint, Prisma, Firebase, Jira.}
\resumeSubItem{Knowledge}
{Linux, CI/CD, UI/UX, Cyberbotics: Webots, VMWare, VirtualBox, Data Science, Agile.}
\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Skillsprint}{Boulder, CO}
{Founding Software Engineer}{November 2022 - Present}
\resumeItemListStart
\resumeItem{Advanced Authentication Development}
{Engineered a robust authentication system using JWT tokens and Nest.js route guards, significantly bolstering application security and ensuring secure user access.}
\resumeItem{Technological Integration Mastery}
{Successfully integrated and optimized diverse tech stack (Prisma, Swagger, Prettier, PostgreSQL) for efficient backend service.}
\resumeItem{CI/CD}
{Implemented GitHub Actions to automate testing and cloud deployment, streamlining the CD pipeline to Vercel for frontend and AWS EC2 for backend services, enhancing development agility and reliability.}
\resumeItem{UI/UX Leadership}
{Led the design efforts for the Athena project's user interface and user experience (UI/UX) by crafting comprehensive wireframes using Figma and MUI components.}
\resumeItemListEnd

\resumeSubheading
{Blueprint}{Boulder, CO}
{Infrastructure Lead and Software Engineer}{January 2023 - Present}
\resumeItemListStart
\resumeItem{AWS Amplify Deployment}
{Spearheaded the deployment of Blueprint's website on AWS Amplify, optimizing its scalability, reliability, and performance, resulting in a robust and highly available web infrastructure.}
\resumeItem{SSL and Domains}
{Implemented SSL certificates and configured domain settings, enhancing the website's security and trustworthiness, resulting in improved user confidence and SEO rankings.}
\resumeItem{Gatsby to Next.js Migration}
{Led successful migration of a Gatsby.js project to a Next.js framework, improving website performance and scalability while ensuring a seamless user experience.}
\resumeItem{SQL Migration}
{Designed, developed, and executed a migration script using MySQL to transition from legacy to a new database schema, demonstrating deep technical expertise and attention to detail.}
\resumeItem{End-to-End Testing}
{Managed end-to-end testing and validation of migration process, effectively ensuring data integrity, minimal downtime, and zero data loss during the transition.}
\resumeItemListEnd

\resumeSubheading
{ACM@UIUC}{Urbana-Champaign, IL}
{Chair of SIG Mobile}{May 2021 - May 2022}
\resumeItemListStart
\resumeItem{Mobile App Development Leadership}
{Led and participated in full-stack development of a mobile app using Flutter for the frontend and Express for the backend.}
\resumeItem{Cutting-Edge Website Development}
{Pioneered the design and development of a dynamic and responsive website for SIGMobile, harnessing the power of Nuxt.js 3 to elevate the club's online presence and accessibility.}
\resumeItem{Knowledge Sharing and Skill Enhancement}
{Fostered continuous learning through organizing and leading Flutter educational sessions, enabling club members to enhance coding skills and adopt industry best practices.}
\resumeItemListEnd

\resumeSubheading
{Costa Rica Customs Research}{Urbana-Champaign, IL}
{Software Engineer Researcher}{September 2021 - December 2021}
\resumeItemListStart
\resumeItem{Quality Assurance}
{Diagnosed and resolved critical application issues, proactively enhancing user experience by systematically identifying and addressing input-related errors.}
\resumeItem{Innovative Feature Development}
{Spearheaded the conceptualization and integration of a cutting-edge User Experience (UX) system, elevating the overall usability and satisfaction of the application.}
\resumeItem{Cross-Functional Collaboration}
{Orchestrated productive collaboration with a diverse team of 4 members, harmonizing efforts to achieve project objectives and timelines.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart
\resumeSubItem{2\textsuperscript{nd} Place at HackCU}
{Engineered a Chess-Street Fighter-inspired Unity game in just 24 hours, showcasing adaptability and creativity.}
\resumeSubItem{Mobile App}
{Conceptualized and crafted an open source, dynamic mobile application powered by AniList's GraphQL API, establishing a cutting-edge platform for users to access and interact with anime-related content.}
\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
